---
title: "PaleoAnth SiteMaps"
---

## About

This repository and website serve as a means to share, create, and visualize spatiotemporal information related to hominin sites in the middle and late Pleistocene. The information below includes both an interactive map and a dynamic table. Tables and maps are able to be exported into a word processor for manuscript development. 

## Map of Mid- to Late-Pleistocene hominin sites

```{r}
#| cache = FALSE
knitr::read_chunk('Mapcode.r')
```


```{r,echo=FALSE}
library(leaflet)
```

```{r,echo=FALSE}
library(leaflegend)
```

```{r,echo=FALSE}
library(htmltools)
```

I need to set some parameters for how I want the map to be designed. The primary tools used are found in the `leaflets` package and associated additions (`leaflet.providers` and `leaflegend`). We need to allow tags to be used from the htmltools package for altering icon dynamics. This is done also for developing the map title and legend (if desired). For more details visit https://roh.engineering/posts/2021/05/map-symbols-and-size-legends-for-leaflet/

```{r, Loaddata}
```

```{r, Loadmap}
```

```{r, Loadtable}
```