---
title: "PaleoAnth SiteMaps"
---

## About

This repository and website serve as a means to share, create, and visualize spatiotemporal information related to hominin sites throughout the Pleistocene. The information below includes both an interactive map and a dynamic table. Tables and maps are able to be exported into a word processor for manuscript development. 

## Map building

I'm using a couple of packages to bring these maps to life. These laregly include `leaflet` (along with its add-ons) and the `htmltools` package. These operations have specfic parameters to be established which are detailed below. 

```{r}
#| cache = FALSE
knitr::read_chunk('Mapcode.r')
```


```{r,echo=FALSE}
library(leaflet)
```

```{r,echo=FALSE}
library(leaflegend)
```

```{r,echo=FALSE}
library(htmltools)
```

```{r, Loaddata}
```
## Chibanian and Late Pleistocene

The data presented in this map and table was taken from my earlier work on the topic. I used this material mostly to figure out the map building process. The table I included (which the map is drawn from) is intentionally simplistic. If we are using this page for sharing/visualizing information, we can keep all tables used for this pretty simple. See below, however, for how a more comprehensive table would appear. 

```{r, Loadmap}
```

```{r, Loadtable}
```

## Early Pleistocene Map

The data for this map and table were taken from the google doc shared with the group. I additionally added the Lat/Long, Number, and Ref. columns for ease of translation. 

```{r, Loaddata2}
```

```{r, Loadmap2}
```

## Early Pleistocene Sites

This is a more comprehensive table than I originally built. As long as all of the information is in an Excel file (.csv), I can include or omit information with ease. 

```{r, Loadtable2}
```